Report - Latest Rodent Data

### 2018-02-15 index.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions)
plot(sp_predict)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
sp_predict = plot_species_forecast(sp_predictions,title=paste0(sp_predictions$forecast_date[2], ": All plots"))
plot(sp_predict)
```
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

### 2018-02-15 report.Rmd

---
title: "Report - Latest Rodent Data"
---
Here's the most recent data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("tools/forecast_tools.R")
library(portalr)

@@

sp_predict = plot_species_forecast(sp_predictions)  
sp_predict = sp_predict + geom_point(data = joined_data, mapping = aes(x = abundance, y = species),
             color = "blue")
plot(sp_predict)
```

>>>>

---
title: "Report - Latest Rodent Data"
---
Here's the most recent actual data (blue) compared to the forecast performed right before data collection (black, with error bars)
```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("tools/forecast_tools.R")
library(portalr)

# get most recent rodent data
rodents = abundance("repo", shape='flat', level='treatment')
most_recent_period = max(rodents$period)
observed = dplyr::filter(rodents, period == most_recent_period, treatment=='control')

ensemble = dplyr::filter(data, level == 'Controls', model == 'Ensemble', newmoonnumber==moon_code)
sp_predictions = get_sp_predicts(ensemble, 'Controls', lead_time = 1)

sp_predict = plot_species_forecast(sp_predictions,title=paste0(sp_predictions$forecast_date[2], ": Control plots"))  
sp_predict = sp_predict + geom_point(data = joined_data, mapping = aes(x = abundance, y = species),
             color = "blue")
plot(sp_predict)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("tools/forecast_tools.R")
library(portalr)

@@

sp_predict = plot_species_forecast(sp_predictions,title=paste0(sp_predictions$forecast_date[2], ": All plots"))  
sp_predict = sp_predict + geom_point(data = joined_data, mapping = aes(x = abundance, y = species),
             color = "blue")
plot(sp_predict)
```
